### 2021-09-16 sections/appendix/descrete_event_simulation/main.tex
Finish up How-to guide

For every service completion Ciw stores all data records in a simulation 
object~\cite{ciwpython}.
The records that are stored are the following:

% TODO: Maybe move this to reference 
\begin{multicols}{2}
    \begin{itemize}
        \item \textbf{id\_number} \(\in R\).
        \item \textbf{customer\_class} \(= 0\)
        \item \textbf{node} \(= \{0, 1, 2, -1 \} \)
        \item \textbf{arrival\_date} \( \in R^+ \)
        \item \textbf{waiting\_time} \( \in R^+ \)
        \item \textbf{service\_start\_date} \( \in R^+ \)
        \item \textbf{service\_time} \( \in R^+ \)
        \item \textbf{service\_end\_time} \( \in R^+ \)
        \item \textbf{time\_blocked} \( \in R^+ \)
        \item \textbf{exit\_date} \( \in R^+ \)
        \item \textbf{destination} \( = \{1, 2, -1\} \)
        \item \textbf{queue\_size\_at\_arrival} \( \in N \)
        \item \textbf{queue\_size\_at\_departure} \( \in N \)
    \end{itemize}
\end{multicols}

@@

% TODO: Fix code for proportion of individuals within time target

% Run multiple simulation results
% Show all possible arguments
% Get all performance measures

@@

% This discrete event simulation model was built in python and can be installed by 
% running the following command in the terminal:

% Having installed the package, the following script can be used to simulate, and 
% get all required performance measures, of a queueing system with two waiting 
% spaces and two types of individuals for a runtime of 2000 unit time with the 
% following parameters:

% \lstinputlisting[language=Python, style=pystyle]{sections/appendix/descrete_event_simulation/simulation.py}

% The script above shows the outcome of the DES model for a single run.
% To minimise the stochasticity of the simulation, the model can be simulated for 
% numerous trials. 
% The following script can be used to run the simulation for a number of times 
% and get the mean of the waiting, service and blocking times:

% \lstinputlisting[language=Python, style=pystyle]{sections/appendix/descrete_event_simulation/multiple_runs.py}

% Finally, the proportion of individuals within target for multiple runs can be
% calculated by running the following block of code:

% \lstinputlisting[language=Python, style=pystyle]{sections/appendix/descrete_event_simulation/multiple_runs_proportion.py}

>>>>

@@

To get the average proportion of individuals within target, run the following
code:

\begin{lstlisting}[style=pystyle]
    >>> import ambulance_game as abg
    >>> (
    ...     overall_proportion,
    ...     class_1_proportion,
    ...     class_2_proportion,
    ... ) = abg.simulation.
    get_mean_proportion_of_individuals_within_target_for_multiple_runs(    
    ...     lambda_1=3,
    ...     lambda_2=2,
    ...     mu=1,
    ...     num_of_servers=6,
    ...     threshold=10,
    ...     system_capacity=20,
    ...     buffer_capacity=10,
    ...     seed_num=0,
    ...     num_of_trials=10,
    ...     runtime=2000,
    ...     target=1,
    ... )
\end{lstlisting}
% TODO: Fix code for proportion of individuals within time target

@@

\subsection{Explanation}

For every service completion Ciw stores all data records in a simulation 
object~\cite{ciwpython}.
For the specific library the records that are stored, along with the 
range of values that they can take are as follows:

\begin{multicols}{2}
    \begin{itemize}
        \item \textbf{id\_number} \(\in R\).
        \item \textbf{customer\_class} \(= 0\)
        \item \textbf{node} \(= \{0, 1, 2, -1 \} \)
        \item \textbf{arrival\_date} \( \in R^+ \)
        \item \textbf{waiting\_time} \( \in R^+ \)
        \item \textbf{service\_start\_date} \( \in R^+ \)
        \item \textbf{service\_time} \( \in R^+ \)
        \item \textbf{service\_end\_time} \( \in R^+ \)
        \item \textbf{time\_blocked} \( \in R^+ \)
        \item \textbf{exit\_date} \( \in R^+ \)
        \item \textbf{destination} \( = \{1, 2, -1\} \)
        \item \textbf{queue\_size\_at\_arrival} \( \in N \)
        \item \textbf{queue\_size\_at\_departure} \( \in N \)
    \end{itemize}
\end{multicols}
